---
title: "Image Database for Everyday Affective Spaces (IDEAS)"
output:
  word_document: default
  html_document: default
header-includes:
  - \usepackage{fontspec}
  - \setmainfont{Times New Roman}
date: "2025-07-11"
---
This script reproduces all statistical analyses, tables, and figures in the IDEAS study. Please cite the article if you make use of this code.

# Start

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
knitr::opts_chunk$set(fig.width = 10, fig.height = 10)


library("caret")
library("ggplot2")
library("dplyr")
library("gridExtra")
library("emmeans")
library("lmerTest")
library("lmtest")
library("tidyr")
library("gam")
library("mgcv")
library("gt")
library("lm.beta")
library("jtools")
library("cowplot")
library("car")
library("patchwork")

# Useful functions to simplify things
source(".\\utils.R")

# Load Affect Data
data_all <- read.csv("..\\Mean Data\\combined_data.csv")
data_all <- data_all[, colnames(data_all) %in% c("image", "tense", "energetic", "valence", "approach", "room_type", "valence_std", "tense_std", "energetic_std", "approach_std")]
data_all$valence <- data_all$valence- 4
data_all$tense <- data_all$tense- 4
data_all$energetic <- data_all$energetic- 4
data_all$approach <- data_all$approach- 4
data_all$I_valence <- ifelse(data_all$valence >= 0, 1, 0) 
data_all$I_energetic <- ifelse(data_all$energetic >= 0, 1, 0)
data_all$I_tense <- ifelse(data_all$tense >= 0, 1, 0) 
data_all$I_approach <- ifelse(data_all$approach >= 0, 1, 0)

# Load individual data both for valence and arousal with 
data_valence_demographic <- read.csv("..\\Data for demographic analysis\\valence_demographic.csv")
data_valence_demographic$Age = as.numeric(data_valence_demographic$Age)

data_arousal_demographic <- read.csv("..\\Data for demographic analysis\\arousal_demographic.csv")
data_arousal_demographic$Age = as.numeric(data_arousal_demographic$Age)


# Load demographic data for both valence and arousal studies, and combine them into one.
data_valence_only_demographic <- read.csv("..\\Data for demographic analysis\\valence_demographic_only.csv")
data_arousal_only_demographic <- read.csv("..\\Data for demographic analysis\\arousal_demographic_only.csv")
data_only_demographic <- rbind(data_valence_only_demographic, data_arousal_only_demographic)

# Create folder for visualizations
check_create_directory(".\\Visualizations")

```

# 3. Results - Descriptive Statistics

## Intraclass Correlation Coefficient


```{r, echo = FALSE}
# Calculate ICC scores
icc_scores <- calculate_icc_scores_psych(type = "ICC2k")
knitr::kable(icc_scores,caption = "ICC scores for all dependent variables.")
```

## Descriptive Statistics

```{r, echo = FALSE}
# Calculate descriptive statistics for all dependent variables
desc_table <- data.frame(Variable = c("Valence","Energetic arousal","Tense arousal","Approach-avoidance"),
  
  Mean = c(round(mean(data_all$valence, na.rm = TRUE), 3),
    round(mean(data_all$energetic, na.rm = TRUE), 3),
    round(mean(data_all$tense, na.rm = TRUE), 3),
    round(mean(data_all$approach, na.rm = TRUE), 3)),
  
  SD = c(round(sd(data_all$valence, na.rm = TRUE), 2),
    round(sd(data_all$energetic, na.rm = TRUE), 2),
    round(sd(data_all$tense, na.rm = TRUE), 2),
    round(sd(data_all$approach, na.rm = TRUE), 2))
)
knitr::kable(desc_table,caption = "Descriptive statistics for study variables.")
```


## Correlation Table
```{r, echo = FALSE}
# Calculate person correlation coefficient between all dependent variables
cor_matrix <- cor(data_all[,c("valence", "tense","energetic","approach")])
cor_matrix <- round(cor_matrix, 2)
knitr::kable(cor_matrix,caption = "Correlation Matrix", align = "c")
```

# 3.1 Reliability and Validation of IDEAS

## Equivalence Test

```{r, echo = FALSE}
# Load Data and set upper and lower bounds
valence_approach_data <- read.csv("..\\Data for equivalence testing\\val_app_data.csv")
tense_energetic_data <- read.csv("..\\Data for equivalence testing\\ten_ene_data.csv")

bound_u <- 1
bound_l <- -1
```


### Valence

```{r, echo = FALSE}
valence_model <- lmer(valence ~ study + image + (1 | participant),data = valence_approach_data, REML = TRUE)

L <- rep(0, length(fixef(valence_model)))
L[which(names(fixef(valence_model)) == "studyIDEAS")] <- 1

lower <- contest1D(valence_model, L = L, rhs = bound_l, confint = TRUE)
upper <- contest1D(valence_model, L = L, rhs = bound_u, confint = TRUE)
print("Lower test")
lower
print("Upper test")
upper
```

### Tense Arousal

```{r, echo = FALSE}
tense_model <- lmer(tense ~ study + image + (1 | participant),data = tense_energetic_data, REML = TRUE)

L <- rep(0, length(fixef(tense_model)))
L[which(names(fixef(tense_model)) == "studyIDEAS")] <- 1

lower <- contest1D(tense_model, L = L, rhs = bound_l, confint = TRUE)
upper <- contest1D(tense_model, L = L, rhs = bound_u, confint = TRUE)
print("Lower test")
lower
print("Upper test")
upper

```

### Energetic Arousal

```{r, echo = FALSE}
energetic_model <- lmer(energetic ~ study + image + (1 | participant),data = tense_energetic_data, REML = TRUE)

L <- rep(0, length(fixef(energetic_model)))
L[which(names(fixef(energetic_model)) == "studyIDEAS")] <- 1

lower <- contest1D(energetic_model, L = L, rhs = bound_l, confint = TRUE)
upper <- contest1D(energetic_model, L = L, rhs = bound_u, confint = TRUE)

print("Lower test")
lower
print("Upper test")
upper
```

### Approach-avoidance

```{r, echo = FALSE}
approach_model <- lmer(approach ~ study + image + (1 | participant),data = valence_approach_data, REML = TRUE)

L <- rep(0, length(fixef(approach_model)))
L[which(names(fixef(approach_model)) == "studyIDEAS")] <- 1

lower <- contest1D(approach_model, L = L, rhs = bound_l, confint = TRUE)
upper <- contest1D(approach_model, L = L, rhs = bound_u, confint = TRUE)

print("Lower test")
lower
print("Upper test")
upper
```

```{r, echo = FALSE}
# Calculate skewness and kurtosis for all the models used for equivalence testing.
skew_kurt_table <- bind_rows(
  Valence = round(extract_skewness_kurtosis(valence_model),2),
  Approach_Avoidance = round(extract_skewness_kurtosis(approach_model),2),
  Tense_Arousal = round(extract_skewness_kurtosis(tense_model),2),
  Energetic_Arousal = round(extract_skewness_kurtosis(energetic_model),2),
  .id = "Dependent Variable"
)
knitr::kable(skew_kurt_table, col.names = c("Outcome", "Skewness", "Kurtosis"), caption = "Residual skewness and kurtosis for each model")
```

### Table 2

```{r, echo = FALSE}
# Results of the LMM models that were used to assess validity for all dependent variables. 
table_valence <- make_effects_table(anova(valence_model), "Valence")
table_approach   <- make_effects_table(anova(approach_model), "Approach-avoidance")
table_tense   <- make_effects_table(anova(tense_model), "Tense Arousal")
table_energetic   <- make_effects_table(anova(energetic_model), "Energetic Arousal")

final_table <- rbind(table_valence,table_approach, table_tense, table_energetic)

knitr::kable(
  final_table,
  align = c("l", "l", "r", "r", "r", "r"),  # left for text columns, right for numbers
  caption = "Fixed Effects from Linear Mixed Models"
)
```
# 3.2 Examining the Relationship Between Affective Responses

# Building Models for all dependent variables

```{r,echo=FALSE}
model1_t_v <- lm(tense ~ 1, data = data_all) # Null 
model2_t_v <- lm(tense ~ valence, data = data_all) #Linear
model3_t_v <- lm(tense ~ abs(valence), data = data_all) #Symmetric V
model4_t_v <- lm(tense ~ abs(valence) + I_valence, data = data_all) # Positivity Offset (different intercepts, same slope)
model5_t_v <- lm(tense ~ abs(valence) + (abs(valence):I_valence), data = data_all) # Negativity Bias (same intercept, different slopes)
model6_t_v <- lm(tense ~ abs(valence) + I_valence + (abs(valence)*I_valence), data = data_all) # Full Asymmetry (offset + bias)
model7_t_v <- gam(tense ~ s(valence), data = data_all) # #Non-parametric

model1_v_t <- lm(valence ~ 1, data = data_all)
model2_v_t <- lm(valence ~ tense, data = data_all)
model3_v_t <- lm(valence ~ abs(tense), data = data_all)
model4_v_t <- lm(valence ~ abs(tense) + I_tense, data = data_all)
model5_v_t <- lm(valence ~ abs(tense) + (abs(tense):I_tense), data = data_all)
model6_v_t <- lm(valence ~ abs(tense) + I_tense + (abs(tense)*I_tense), data = data_all)
model7_v_t <- gam(valence ~ s(tense), data = data_all)

model1_e_v <- lm(energetic ~ 1, data = data_all)
model2_e_v <- lm(energetic ~ valence, data = data_all)
model3_e_v <- lm(energetic ~ abs(valence), data = data_all)
model4_e_v <- lm(energetic ~ abs(valence) + I_valence, data = data_all)
model5_e_v <- lm(energetic ~ abs(valence) + (abs(valence): I_valence), data = data_all)
model6_e_v <- lm(energetic ~ abs(valence) + I_valence + (abs(valence)*I_valence), data = data_all)
model7_e_v <- gam(energetic ~ s(valence), data = data_all)

model1_v_e <- lm(valence ~ 1, data = data_all)
model2_v_e <- lm(valence ~ energetic, data = data_all)
model3_v_e <- lm(valence ~ abs(energetic), data = data_all)
model4_v_e <- lm(valence ~ abs(energetic) + I_energetic, data = data_all)
model5_v_e <- lm(valence ~ abs(energetic) + (abs(energetic):I_energetic), data = data_all)
model6_v_e <- lm(valence ~ abs(energetic) + I_energetic + (abs(energetic)*I_energetic), data = data_all)
model7_v_e <- gam(valence ~ s(energetic), data = data_all)

model1_e_t <- lm(energetic ~ 1, data = data_all)
model2_e_t <- lm(energetic ~ tense, data = data_all)
model3_e_t <- lm(energetic ~ abs(tense), data = data_all)
model4_e_t <- lm(energetic ~ abs(tense) + I_tense, data = data_all)
model5_e_t <- lm(energetic ~ abs(tense) + (abs(tense):I_tense), data = data_all)
model6_e_t <- lm(energetic ~ abs(tense) + I_tense + (abs(tense)*I_tense), data = data_all)
model7_e_t <- gam(energetic ~ s(tense), data = data_all)

model1_t_e <- lm(tense ~ 1, data = data_all)
model2_t_e <- lm(tense ~ energetic, data = data_all)
model3_t_e <- lm(tense ~ abs(energetic), data = data_all)
model4_t_e <- lm(tense ~ abs(energetic) + I_energetic, data = data_all)
model5_t_e <- lm(tense ~ abs(energetic) + (abs(energetic):I_energetic), data = data_all)
model6_t_e <- lm(tense ~ abs(energetic) + I_energetic + (abs(energetic)*I_energetic), data = data_all)
model7_t_e <- gam(tense ~ s(energetic), data = data_all)
```

#### Table 4. 

```{r,echo = FALSE, warning = FALSE, message = FALSE}
# Get posterior probabilities for all models.
posterior_probs_t_v <- get_posterior_probs(model1_t_v,model2_t_v,model3_t_v, model4_t_v, model5_t_v, model6_t_v, model7_t_v)
posterior_probs_v_t <- get_posterior_probs(model1_v_t,model2_v_t,model3_v_t, model4_v_t, model5_v_t, model6_v_t, model7_v_t)
posterior_probs_e_v <- get_posterior_probs(model1_e_v,model2_e_v,model3_e_v, model4_e_v, model5_e_v, model6_e_v, model7_e_v)
posterior_probs_v_e <- get_posterior_probs(model1_v_e,model2_v_e,model3_v_e, model4_v_e, model5_v_e, model6_v_e, model7_v_e)
posterior_probs_t_e <- get_posterior_probs(model1_t_e,model2_t_e,model3_t_e, model4_t_e, model5_t_e, model6_t_e, model7_t_e)
posterior_probs_e_t <- get_posterior_probs(model1_e_t,model2_e_t,model3_e_t, model4_e_t, model5_e_t, model6_e_t, model7_e_t)

# Create Table 4
data <- tibble::tibble(
  Relationship = c("Tense - Valence", "Valence - Tense", "Energetic-Valence","Valence-Energetic", "Tense-Energetic", "Energetic-Tense"),
  # Model 1
  BIC1 = c(
    round(BIC(model1_t_v)), round(BIC(model1_v_t)), round(BIC(model1_e_v)),
    round(BIC(model1_v_e)), round(BIC(model1_t_e)), round(BIC(model1_e_t))
  ),
  R21 = rep(0.00, 6),
  PP1 = round(c(
    posterior_probs_t_v[1], posterior_probs_v_t[1], posterior_probs_e_v[1],
    posterior_probs_v_e[1], posterior_probs_t_e[1], posterior_probs_e_t[1]
  ), 2),

  # Model 2
  BIC2 = c(
    round(BIC(model2_t_v)), round(BIC(model2_v_t)), round(BIC(model2_e_v)),
    round(BIC(model2_v_e)), round(BIC(model2_t_e)), round(BIC(model2_e_t))
  ),
  R22 = c(
    round(summary(model2_t_v)$r.squared, 2), round(summary(model2_v_t)$r.squared, 2), round(summary(model2_e_v)$r.squared, 2),
    round(summary(model2_v_e)$r.squared, 2), round(summary(model2_t_e)$r.squared, 2), round(summary(model2_e_t)$r.squared, 2)
  ),
  PP2 = round(c(
    posterior_probs_t_v[2], posterior_probs_v_t[2], posterior_probs_e_v[2],
    posterior_probs_v_e[2], posterior_probs_t_e[2], posterior_probs_e_t[2]
  ), 2),

  # Model 3
  BIC3 = c(
    round(BIC(model3_t_v)), round(BIC(model3_v_t)), round(BIC(model3_e_v)),
    round(BIC(model3_v_e)), round(BIC(model3_t_e)), round(BIC(model3_e_t))
  ),
  R23 = c(
    round(summary(model3_t_v)$r.squared, 2), round(summary(model3_v_t)$r.squared, 2), round(summary(model3_e_v)$r.squared, 2),
    round(summary(model3_v_e)$r.squared, 2), round(summary(model3_t_e)$r.squared, 2), round(summary(model3_e_t)$r.squared, 2)
  ),
  PP3 = round(c(
    posterior_probs_t_v[3], posterior_probs_v_t[3], posterior_probs_e_v[3],
    posterior_probs_v_e[3], posterior_probs_t_e[3], posterior_probs_e_t[3]
  ), 2),

  # Model 4
  BIC4 = c(
    round(BIC(model4_t_v)), round(BIC(model4_v_t)), round(BIC(model4_e_v)),
    round(BIC(model4_v_e)), round(BIC(model4_t_e)), round(BIC(model4_e_t))
  ),
  R24 = c(
    round(summary(model4_t_v)$r.squared, 2), round(summary(model4_v_t)$r.squared, 2), round(summary(model4_e_v)$r.squared, 2),
    round(summary(model4_v_e)$r.squared, 2), round(summary(model4_t_e)$r.squared, 2), round(summary(model4_e_t)$r.squared, 2)
  ),
  PP4 = round(c(
    posterior_probs_t_v[4], posterior_probs_v_t[4], posterior_probs_e_v[4],
    posterior_probs_v_e[4], posterior_probs_t_e[4], posterior_probs_e_t[4]
  ), 2),

  # Model 5
  BIC5 = c(
    round(BIC(model5_t_v)), round(BIC(model5_v_t)), round(BIC(model5_e_v)),
    round(BIC(model5_v_e)), round(BIC(model5_t_e)), round(BIC(model5_e_t))
  ),
  R25 = c(
    round(summary(model5_t_v)$r.squared, 2), round(summary(model5_v_t)$r.squared, 2), round(summary(model5_e_v)$r.squared, 2),
    round(summary(model5_v_e)$r.squared, 2), round(summary(model5_t_e)$r.squared, 2), round(summary(model5_e_t)$r.squared, 2)
  ),
  PP5 = round(c(
    posterior_probs_t_v[5], posterior_probs_v_t[5], posterior_probs_e_v[5],
    posterior_probs_v_e[5], posterior_probs_t_e[5], posterior_probs_e_t[5]
  ), 2),

  # Model 6
  BIC6 = c(
    round(BIC(model6_t_v)), round(BIC(model6_v_t)), round(BIC(model6_e_v)),
    round(BIC(model6_v_e)), round(BIC(model6_t_e)), round(BIC(model6_e_t))
  ),
  R26 = c(
    round(summary(model6_t_v)$r.squared, 2), round(summary(model6_v_t)$r.squared, 2), round(summary(model6_e_v)$r.squared, 2),
    round(summary(model6_v_e)$r.squared, 2), round(summary(model6_t_e)$r.squared, 2), round(summary(model6_e_t)$r.squared, 2)
  ),
  PP6 = round(c(
    posterior_probs_t_v[6], posterior_probs_v_t[6], posterior_probs_e_v[6],
    posterior_probs_v_e[6], posterior_probs_t_e[6], posterior_probs_e_t[6]
  ), 2),

  # Model 7
  BIC7 = c(
    round(BIC(model7_t_v)), round(BIC(model7_v_t)), round(BIC(model7_e_v)),
    round(BIC(model7_v_e)), round(BIC(model7_t_e)), round(BIC(model7_e_t))
  ),
  R27 = c(
    round(summary(model7_t_v)$r.sq, 2), round(summary(model7_v_t)$r.sq, 2), round(summary(model7_e_v)$r.sq, 2),
    round(summary(model7_v_e)$r.sq, 2), round(summary(model7_t_e)$r.sq, 2), round(summary(model7_e_t)$r.sq, 2)
  ),
  PP7 = round(c(
    posterior_probs_t_v[7], posterior_probs_v_t[7], posterior_probs_e_v[7],
    posterior_probs_v_e[7], posterior_probs_t_e[7], posterior_probs_e_t[7]
  ), 2)
)
# Create the table
gt_table <- data %>%
  gt() %>%
  tab_spanner(label = "Model 1\nIndependence", columns = c(BIC1, R21, PP1)) %>%
  tab_spanner(label = "Model 2\nLinear\nRelation", columns = c(BIC2, R22, PP2)) %>%
  tab_spanner(label = "Model 3\nSymmetric V", columns = c(BIC3, R23, PP3)) %>%
  tab_spanner(label = "Model 4\nAsymmetric V\npositivity offset", columns = c(BIC4, R24,PP4)) %>%
  tab_spanner(label = "Model 5\nAsymmetric V\nnegativity bias", columns = c(BIC5, R25,PP5)) %>%
  tab_spanner(label = "Model 6\nAsymmetric V\npositivity offset\n+ negativity bias", columns = c(BIC6, R26,PP6)) %>%
  tab_spanner(label = "Model 7\nNonparametric", columns = c(BIC7, R27,PP7)) %>%
  cols_label(
    BIC1 = "BIC", R21 = "R2", PP1 = "PP",
    BIC2 = "BIC", R22 = "R2", PP2 = "PP",
    BIC3 = "BIC", R23 = "R2", PP3 = "PP",
    BIC4 = "BIC", R24 = "R2", PP4 = "PP",
    BIC5 = "BIC", R25 = "R2", PP5 = "PP",
    BIC6 = "BIC", R26 = "R2", PP6 = "PP",
    BIC7 = "BIC", R27 = "R2", PP7 = "PP"
  ) %>%
  tab_header(title = "Model Comparison Table")
gt_table
```

#### Figure 3

```{r, echo = FALSE, warning=FALSE}
# Code to generate figure 3
alpha_val <- 0.95
alpha_point <- 0.05
size <- 1.1
alpha_hvline <- 1
title_size <- 14
tick_size <- 13
color_palette <- c("#F0E442", "#CC79A7", "#117733","#009E73", "#CC79A7", "#CC79A7","#0072B2")
# c("model_1","model_2","model_3","model_4","model_5","model_6","model_7")
# Tense-Valence
predictions <- pred_scores(list(model1_t_v, model2_t_v, model3_t_v, model4_t_v, model5_t_v, model6_t_v, model7_t_v), data_all$valence, list("valence", "I_valence"), 2000)
plot_t_v <- plot_data(data_all, c('valence', 'tense'), c("Valence", "Tense Arousal"), alpha_point, alpha_hvline, tick_size, title_size)
plot_t_v <- add_lines(data = predictions, model_names = c("model_5"), plot = plot_t_v, x_col = "valence", color_palette = color_palette,size = size, alpha_val = alpha_val)
plot_t_v <- plot_t_v + labs(tag = "(a)") +
  theme(plot.tag = element_text(size = 14, face = "bold"), plot.tag.position = c(0.02, 1.02), plot.margin = margin(t = 15, r = 5, b = 5, l = 5))

# Valence-Tense
predictions <- pred_scores(list(model1_v_t, model2_v_t, model3_v_t, model4_v_t, model5_v_t, model6_v_t, model7_v_t), data_all$tense, list("tense", "I_tense"), 2000)
plot_v_t <- plot_data(data_all, c('tense', 'valence'), c("Tense Arousal", "Valence"), alpha_point, alpha_hvline, tick_size, title_size)
plot_v_t <- add_lines(data = predictions, model_names = c("model_2"), plot = plot_v_t, x_col = "tense", color_palette = color_palette,size = size, alpha_val = alpha_val)
plot_v_t <- plot_v_t + labs(tag = "(b)") +
  theme(plot.tag = element_text(size = 14, face = "bold"), plot.tag.position = c(0.02, 1.02), plot.margin = margin(t = 15, r = 5, b = 5, l = 5))


# Energetic - Valence
predictions <- pred_scores(list(model1_e_v, model2_e_v, model3_e_v, model4_e_v, model5_e_v, model6_e_v, model7_e_v), data_all$valence, list("valence", "I_valence"), 2000)
plot_e_v <- plot_data(data_all, c('valence', 'energetic'), c("Valence", "Energetic Arousal"), alpha_point, alpha_hvline, tick_size, title_size)
plot_e_v <- add_lines(data = predictions, model_names = c("model_3"), plot = plot_e_v, x_col = "valence", color_palette = color_palette,size = size, alpha_val = alpha_val)
plot_e_v <- plot_e_v + labs(tag = "(c)") +
  theme(plot.tag = element_text(size = 14, face = "bold"), plot.tag.position = c(0.02, 1.02), plot.margin = margin(t = 15, r = 5, b = 5, l = 5))

# Valence - Energetic
predictions <- pred_scores(list(model1_v_e, model2_v_e, model3_v_e, model4_v_e, model5_v_e, model6_v_e, model7_v_e), data_all$energetic, list("energetic", "I_energetic"), 2000)
plot_v_e <- plot_data(data_all, c('energetic', 'valence'), c("Energetic Arousal", "Valence"), alpha_point, alpha_hvline, tick_size, title_size)
plot_v_e <- add_lines(data = predictions, model_names = c("model_3"), plot = plot_v_e, x_col = "energetic", color_palette = color_palette,size = size, alpha_val = alpha_val)
plot_v_e <- plot_v_e + labs(tag = "(d)") +
  theme(plot.tag = element_text(size = 14, face = "bold"), plot.tag.position = c(0.02, 1.02), plot.margin = margin(t = 15, r = 5, b = 5, l = 5))

# Tense - Energetic
predictions <- pred_scores(list(model1_t_e, model2_t_e, model3_t_e, model4_t_e, model5_t_e, model6_t_e, model7_t_e), data_all$energetic, list("energetic", "I_energetic"), 2000)
plot_t_e <- plot_data(data_all, c('energetic', 'tense'), c("Energetic Arousal", "Tense Arousal"), alpha_point, alpha_hvline, tick_size, title_size)
plot_t_e <- add_lines(data = predictions, model_names = c("model_7"), plot = plot_t_e, x_col = "energetic", color_palette = color_palette,size = size, alpha_val = alpha_val)
plot_t_e <- plot_t_e + labs(tag = "(e)") +
  theme(plot.tag = element_text(size = 14, face = "bold"), plot.tag.position = c(0.02, 1.02), plot.margin = margin(t = 15, r = 5, b = 5, l = 5))

# Energetic - Tense
predictions <- pred_scores(list(model1_e_t, model2_e_t, model3_e_t, model4_e_t, model5_e_t, model6_e_t, model7_e_t), data_all$tense, list("tense", "I_tense"), 2000)
plot_e_t <- plot_data(data_all, c('tense', 'energetic'), c("Tense Arousal", "Energetic Arousal"), alpha_point, alpha_hvline, tick_size, title_size)
plot_e_t <- add_lines(data = predictions, model_names = c("model_7"), plot = plot_e_t, x_col = "tense", color_palette = color_palette,size = size, alpha_val = alpha_val)
plot_e_t <- plot_e_t + labs(tag = "(f)") +
  theme(plot.tag = element_text(size = 14, face = "bold"), plot.tag.position = c(0.02, 1.02), plot.margin = margin(t = 15, r = 5, b = 5, l = 5))


final_plot_all <- gridExtra::grid.arrange(plot_t_v,plot_v_t, plot_e_v, plot_v_e, plot_t_e, plot_e_t, ncol=2, nrow=3)
ggsave(file=".\\Visualizations\\affective_space_plot.svg", plot=final_plot_all, width=10, height=10)


```

#### Figure 3 Supplementary 

```{r, echo = FALSE}
# Code to generate figure in supplementary material S3
alpha_val <- 0.9
alpha_point <- 0.05
size <- 1.1
alpha_hvline <- 1
title_size <- 14
tick_size <- 13
color_palette <- c("black", "#CC79A7", "#CCC23B","#009E73", "red", "#D86002","#0072B2")
# c("model_1","model_2","model_3","model_4","model_5","model_6","model_7")
# Tense-Valence
predictions <- pred_scores(list(model1_t_v, model2_t_v, model3_t_v, model4_t_v, model5_t_v, model6_t_v, model7_t_v), data_all$valence, list("valence", "I_valence"), 2000)
plot_t_v <- plot_data(data_all, c('valence', 'tense'), c("Valence", "Tense Arousal"), alpha_point, alpha_hvline, tick_size, title_size)
plot_t_v <- add_lines(data = predictions, model_names = c("model_1","model_2","model_3","model_4","model_5","model_6","model_7"), plot = plot_t_v, x_col = "valence", color_palette = color_palette,size = size, alpha_val = alpha_val)
plot_t_v <- plot_t_v + labs(tag = "(a)") +
  theme(plot.tag = element_text(size = 14, face = "bold"), plot.tag.position = c(0.02, 1.02), plot.margin = margin(t = 15, r = 5, b = 5, l = 5))

# Valence-Tense
predictions <- pred_scores(list(model1_v_t, model2_v_t, model3_v_t, model4_v_t, model5_v_t, model6_v_t, model7_v_t), data_all$tense, list("tense", "I_tense"), 2000)
plot_v_t <- plot_data(data_all, c('tense', 'valence'), c("Tense Arousal", "Valence"), alpha_point, alpha_hvline, tick_size, title_size)
plot_v_t <- add_lines(data = predictions, model_names = c("model_1","model_2","model_3","model_4","model_5","model_6","model_7"), plot = plot_v_t, x_col = "tense", color_palette = color_palette,size = size, alpha_val = alpha_val)
plot_v_t <- plot_v_t + labs(tag = "(b)") +
  theme(plot.tag = element_text(size = 14, face = "bold"), plot.tag.position = c(0.02, 1.02), plot.margin = margin(t = 15, r = 5, b = 5, l = 5))


# Energetic - Valence
predictions <- pred_scores(list(model1_e_v, model2_e_v, model3_e_v, model4_e_v, model5_e_v, model6_e_v, model7_e_v), data_all$valence, list("valence", "I_valence"), 2000)
plot_e_v <- plot_data(data_all, c('valence', 'energetic'), c("Valence", "Energetic Arousal"), alpha_point, alpha_hvline, tick_size, title_size)
plot_e_v <- add_lines(data = predictions, model_names = c("model_1","model_2","model_3","model_4","model_5","model_6","model_7"), plot = plot_e_v, x_col = "valence", color_palette = color_palette,size = size, alpha_val = alpha_val)
plot_e_v <- plot_e_v + labs(tag = "(c)") +
  theme(plot.tag = element_text(size = 14, face = "bold"), plot.tag.position = c(0.02, 1.02), plot.margin = margin(t = 15, r = 5, b = 5, l = 5))

# Valence - Energetic
predictions <- pred_scores(list(model1_v_e, model2_v_e, model3_v_e, model4_v_e, model5_v_e, model6_v_e, model7_v_e), data_all$energetic, list("energetic", "I_energetic"), 2000)
plot_v_e <- plot_data(data_all, c('energetic', 'valence'), c("Energetic Arousal", "Valence"), alpha_point, alpha_hvline, tick_size, title_size)
plot_v_e <- add_lines(data = predictions, model_names = c("model_1","model_2","model_3","model_4","model_5","model_6","model_7"), plot = plot_v_e, x_col = "energetic", color_palette = color_palette,size = size, alpha_val = alpha_val)
plot_v_e <- plot_v_e + labs(tag = "(d)") +
  theme(plot.tag = element_text(size = 14, face = "bold"), plot.tag.position = c(0.02, 1.02), plot.margin = margin(t = 15, r = 5, b = 5, l = 5))

# Tense - Energetic
predictions <- pred_scores(list(model1_t_e, model2_t_e, model3_t_e, model4_t_e, model5_t_e, model6_t_e, model7_t_e), data_all$energetic, list("energetic", "I_energetic"), 2000)
plot_t_e <- plot_data(data_all, c('energetic', 'tense'), c("Energetic Arousal", "Tense Arousal"), alpha_point, alpha_hvline, tick_size, title_size)
plot_t_e <- add_lines(data = predictions, model_names = c("model_1","model_2","model_3","model_4","model_5","model_6","model_7"), plot = plot_t_e, x_col = "energetic", color_palette = color_palette,size = size, alpha_val = alpha_val)
plot_t_e <- plot_t_e + labs(tag = "(e)") +
  theme(plot.tag = element_text(size = 14, face = "bold"), plot.tag.position = c(0.02, 1.02), plot.margin = margin(t = 15, r = 5, b = 5, l = 5))

# Energetic - Tense
predictions <- pred_scores(list(model1_e_t, model2_e_t, model3_e_t, model4_e_t, model5_e_t, model6_e_t, model7_e_t), data_all$tense, list("tense", "I_tense"), 2000)
plot_e_t <- plot_data(data_all, c('tense', 'energetic'), c("Tense Arousal", "Energetic Arousal"), alpha_point, alpha_hvline, tick_size, title_size)
plot_e_t <- add_lines(data = predictions, model_names = c("model_1","model_2","model_3","model_4","model_5","model_6","model_7"), plot = plot_e_t, x_col = "tense", color_palette = color_palette,size = size, alpha_val = alpha_val)
plot_e_t <- plot_e_t + labs(tag = "(f)") +
  theme(plot.tag = element_text(size = 14, face = "bold"), plot.tag.position = c(0.02, 1.02), plot.margin = margin(t = 15, r = 5, b = 5, l = 5))



final_plot_all <- gridExtra::grid.arrange(plot_t_v,plot_v_t, plot_e_v, plot_v_e, plot_t_e, plot_e_t, ncol=2, nrow=3)
ggsave(file=".\\Visualizations\\affective_space_plot_supplamentary.svg", plot=final_plot_all, width=10, height=10)

```
#### Table 5

```{r, echo = FALSE}
# Code to generate table 5
model_approach <- lm(approach ~ valence + valence * tense + valence * energetic, data = data_all)
regression_table(model_approach)
```

## 3.2 Effect of Demographic Variables on Affective and Approach-avoidance responses

```{r, echo = FALSE, message = FALSE, warning=FALSE}
# Predicting affective responses with demographic characteristics
model_valence  <- lmer(data.valence ~  Country.of.residence + Ethnicity.simplified + Sex + Age + Employment.status + (1|Prolific_id) , data = data_valence_demographic) 
model_null_valence <- lmer(data.valence ~ 1 + (1|Prolific_id) + (1|data.img_idx) , data = data_valence_demographic)
#performance::performance(model_null_valence)
anova_valence <- anova(model_valence)

model_approach  <- lmer(data.approach ~  Country.of.residence + Ethnicity.simplified + Sex + Age + Employment.status + (1|Prolific_id), data = data_valence_demographic)
model_null_approach <- lmer(data.approach ~ 1 + (1|Prolific_id), data = data_valence_demographic)
#performance::performance(model_null_approach)
anova_approach <- anova(model_approach)

model_tense <- lmer(data.tense ~  Country.of.residence + Ethnicity.simplified + Sex + Age + Employment.status + (1|Prolific_id), data = data_arousal_demographic)
model_null_tense <- lmer(data.tense ~ 1 + (1|Prolific_id), data = data_arousal_demographic)
#performance::performance(model_null_tense)
anova_tense <- anova(model_tense)

model_energetic <- lmer(data.energetic ~  Country.of.residence + Ethnicity.simplified + Sex + Age + Employment.status + (1|Prolific_id), data = data_arousal_demographic)
model_null_energetic <- lmer(data.energetic ~ 1 + (1|Prolific_id), data = data_arousal_demographic)
#performance::performance(model_null_energetic)
anova_energetic <- anova(model_energetic)
```

```{r, echo = FALSE}
# Calculate skewness and kurtosis for all the models
skew_kurt_table <- bind_rows(
  Valence = round(extract_skewness_kurtosis(model_valence),2),
  Approach_Avoidance = round(extract_skewness_kurtosis(model_approach),2),
  Tense_Arousal = round(extract_skewness_kurtosis(model_tense),2),
  Energetic_Arousal = round(extract_skewness_kurtosis(model_energetic),2),
  .id = "Dependent Variable"
)
knitr::kable(skew_kurt_table, col.names = c("Outcome", "Skewness", "Kurtosis"), caption = "Residual skewness and kurtosis for each model")
```


```{r, echo=FALSE}
# Residuals plot for all dependent variables 
qq_valence     <- qq_plot(residuals(model_valence), "valence")
qq_approach    <- qq_plot(residuals(model_approach), "approach")
qq_tense       <- qq_plot(residuals(model_tense), "tense")
qq_energetic   <- qq_plot(residuals(model_energetic), "energetic")
qq_plot_grid <- (qq_valence + qq_approach) /
                (qq_tense + qq_energetic) +
  plot_annotation(
    title = "Q–Q Plots of Model Residuals",
    theme = theme(
      plot.title = element_text(size = 16, face = "bold", hjust = 0.5)
    )
  )
ggsave(file=".\\Visualizations\\residual_plots.png", plot=qq_plot_grid, width=10, height=10)
```

### Table 6

```{r, echo = FALSE}
# Extract both marginal and conditional R2 and create table 6.
results_table <- bind_rows(
  Valence = extract_r2(model_valence),
  Tense_Arousal = extract_r2(model_tense),
  Energetic_Arousal = extract_r2(model_energetic),
  Approach_Avoidance = extract_r2(model_approach),
  .id = "Outcome"
) 
knitr::kable(
  results_table,
  digits = 2,
  col.names = c("Dependent Variable", "R2 Marginal", "R2 Conditional"),
  caption = "Marginal and Conditional R-squared values for each outcome"
)
```


### Table 7

```{r, echo = FALSE, message = FALSE, warning=FALSE}
# Pairwise comparisons for demographic variables
pairwise_eth <- emmeans(model_valence, "Ethnicity.simplified")
pairwise_eth <- as.data.frame(pairwise_eth)

pairwise_sex <- emmeans(model_valence, "Sex")
pairwise_sex <- as.data.frame(pairwise_sex)
#pairs(pairwise_sex)

pairwise_eth_tense <- emmeans(model_tense, "Ethnicity.simplified")
pairwise_eth_tense <- as.data.frame(pairwise_eth_tense)
```

```{r, echo = FALSE}
# Tables for differences in estimated marginal means.
knitr::kable(pairwise_eth, caption = "Estimated marginal means ethnicity simplified valence")
knitr::kable(pairwise_sex, caption = "Estimated marginal means gender simplified valence")
knitr::kable(pairwise_eth_tense, caption = "Estimated marginal means ethnicity simplified tense arousal")

```


```{r, echo = FALSE, message = FALSE, warning=FALSE}
# Code to generate table 7
table_valence <- make_effects_table(anova_valence, "Valence")
table_approach   <- make_effects_table(anova_approach, "Approach-avoidance")
table_tense   <- make_effects_table(anova_tense, "Tense Arousal")
table_energetic   <- make_effects_table(anova_energetic, "Energetic Arousal")
final_table <- rbind(table_valence,table_approach, table_tense, table_energetic)
knitr::kable(
  final_table,
  booktabs = TRUE,
  align = c("l", "l", "r", "r", "r", "r"),  # left for text columns, right for numbers
  caption = "Fixed Effects from Linear Mixed Models")
```

### Figure 1
```{r, echo = FALSE}
# Code to generate Figure 1
data_only_demographic <- data_only_demographic %>%
  mutate(
    Employment.status = ifelse(Employment.status == "Unemployed (and job seeking)", "Unemployed", Employment.status),
    Employment.status = ifelse(Employment.status == "Not in paid work (e.g. homemaker', 'retired or disabled)", "Not in paid work", Employment.status),
    Employment.status = ifelse(Employment.status == "Due to start a new job within the next month", "Will start soon", Employment.status),
  )

data_only_demographic <- data_only_demographic %>%
  mutate(Region = case_when(
    Country.of.residence %in% c("United Kingdom") ~ "UK",
    Country.of.residence %in% c("South Africa", "Kenya") ~ "Africa",
    Country.of.residence %in% c("China", "India", "Japan", "Vietnam", "Malaysia") ~ "Asia",
    Country.of.residence %in% c("Israel") ~ "Middle East",
    Country.of.residence %in% c("United States", "Canada", "Mexico") ~ "North America",
    Country.of.residence %in% c("Brazil", "Chile") ~ "South America",
    Country.of.residence %in% c("Austria", "Belgium", "Croatia", "Czech Republic", "Denmark", "Estonia",
                   "Finland", "France", "Germany", "Greece", "Hungary", "Italy", "Latvia",
                   "Luxembourg", "Netherlands", "Norway", "Poland", "Portugal", "Slovakia",
                   "Slovenia", "Spain", "Sweden", "Switzerland") ~ "Europe",
    Country.of.residence %in% c("Australia") ~ "Oceania",
    #Country.of.residence %in% c("DATA_EXPIRED") ~ "DATA_EXPIRED",
    TRUE ~ "Other"
  ))

data_only_demographic <- data_only_demographic %>%
  mutate(Nationality_region = case_when(
    Nationality %in% c("United Kingdom", "Ireland") ~ "UK",
    Nationality %in% c("South Africa", "Nigeria", "Zimbabwe", "Egypt", "Kenya", 
                   "Zambia", "Namibia", "Ghana", "Cote d'Ivoire", "Uganda") ~ "Africa",
    Nationality %in% c("India", "China", "Vietnam", "Japan", "Bangladesh", 
                   "Iran", "Nepal", "Philippines", "Malaysia") ~ "Asia",
    Nationality %in% c("Israel", "Lebanon", "Turkey") ~ "Middle East",
    Nationality %in% c("United States", "Canada", "Mexico") ~ "North America",
    Nationality %in% c("Brazil", "Chile", "Venezuela, Bolivarian Republic of") ~ "South America",
    Nationality %in% c("Austria", "Belgium", "Bosnia and Herzegovina", "Bulgaria", "Croatia", 
                   "Czech Republic", "Denmark", "Estonia", "Finland", "France", "Germany", 
                   "Greece", "Hungary", "Italy", "Latvia", "Lithuania", "Luxembourg", 
                   "Netherlands", "Poland", "Portugal", "Romania", "Russian Federation", 
                   "Slovakia", "Slovenia", "Spain", "Sweden", "Switzerland", "Ukraine", 
                   "Albania", "Norway") ~ "Europe",
    Nationality %in% c("Australia") ~ "Oceania",
    #Nationality %in% c("DATA_EXPIRED") ~ "DATA_EXPIRED",
    TRUE ~ "Other"
  ))


tick_size <- 15
title_size <- 15
size_number <- 4.5
hjust_size <- -.1

ethnicity <- ggplot(data_only_demographic[data_only_demographic$Employment.status != "DATA_EXPIRED",], aes(x = Ethnicity.simplified)) +
  geom_bar() +
  stat_count(geom = "text", aes(label = ..count..), hjust = hjust_size, size = size_number, face = "bold") +
  labs(x = "Ethnicity Simplified", y = "Number of Participants") +
  theme_apa() +
  theme(
    axis.text.x  = element_text(size = tick_size),
    axis.text.y  = element_text(size = tick_size),
    axis.title.x = element_text(size = title_size, face = "bold"),
    axis.title.y = element_text(size = title_size, face = "bold")
  ) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  coord_flip()

employment <- ggplot(data_only_demographic[data_only_demographic$Employment.status != "DATA_EXPIRED",], aes(x = Employment.status)) +
  geom_bar() +
  stat_count(geom = "text", aes(label = ..count..), hjust = hjust_size, size = size_number) +
  labs(x = "Employment Status", y = "Number of Participants") +
  theme_apa() +
  theme(
    axis.text.x  = element_text(size = tick_size),
    axis.text.y  = element_text(size = tick_size),
    axis.title.x = element_text(size = title_size, face = "bold"),
    axis.title.y = element_text(size = title_size, face = "bold")
  ) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  coord_flip()

residence <- ggplot(data_only_demographic, aes(x = Region)) +
  geom_bar() +
  stat_count(geom = "text", aes(label = ..count..), hjust = hjust_size, size = size_number) +
  labs(x = "Current Residence", y = "Number of Participants") +
  theme_apa() +
  theme(
    axis.text.x  = element_text(size = tick_size),
    axis.text.y  = element_text(size = tick_size),
    axis.title.x = element_text(size = title_size, face = "bold"),
    axis.title.y = element_text(size = title_size, face = "bold")
  ) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  coord_flip()

nationality <- ggplot(data_only_demographic, aes(x = Nationality_region)) +
  geom_bar() +
  stat_count(geom = "text", aes(label = ..count..), hjust = hjust_size, size = size_number) +
  labs(x = "Nationality", y = "Number of Participants") +
  theme_apa() +
  theme(
    axis.text.x  = element_text(size = tick_size),
    axis.text.y  = element_text(size = tick_size),
    axis.title.x = element_text(size = title_size, face = "bold"),
    axis.title.y = element_text(size = title_size, face = "bold")
  ) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  coord_flip()

# ??
demographic_plot <- (ethnicity + employment) /
                    (residence + nationality)

ggsave(
  file = ".\\Visualizations\\demographic.svg",
  plot = demographic_plot,
  width = 12,
  height = 8
)

demographic_plot
```

## 3.3 Room Type

```{r, echo = FALSE}
# Fit all models and compute both Levene test and Shapiro Wilk test for all dependent variables
anova_valence <- aov(valence ~ room_type, data = data_all) 
anova_approach <- aov(approach ~ room_type, data = data_all) 
anova_tense <- aov(tense ~ room_type, data = data_all)  
anova_energetic <- aov(energetic ~ room_type, data = data_all) 

anova_models <- list(
  valence    = anova_valence,
  approach   = anova_approach,
  tense      = anova_tense,
  energetic  = anova_energetic
)

assumption_table <- data.frame(
  DV = character(),
  Levene_F = numeric(),
  Levene_p = numeric(),
  Shapiro_W = numeric(),
  Shapiro_p = numeric(),
  stringsAsFactors = FALSE
)

for (dv in names(anova_models)) {
  
  model <- anova_models[[dv]]
  
  # Levene’s test
  lev <- leveneTest(
    formula(model),
    data = model$model
  )
  
  # Shapiro–Wilk test on residuals
  shap <- shapiro.test(residuals(model))
  
  # Store results
  assumption_table <- rbind(
    assumption_table,
    data.frame(
      DV = dv,
      Levene_F = lev$`F value`[1],
      Levene_p = lev$`Pr(>F)`[1],
      Shapiro_W = shap$statistic,
      Shapiro_p = shap$p.value
    )
  )
}

knitr::kable(assumption_table, caption = "Levene and Shapiro Wilk Test Room Type",align = "c")
```

```{r,echo = FALSE}
# Fir Welch's ANOVA for all dependent variables and calculate partial eta squared for all models.
anova_valence <- oneway.test(valence ~ factor(room_type), data = data_all, var.equal = FALSE) 
anova_approach <- oneway.test(approach ~ factor(room_type), data = data_all, var.equal = FALSE) 
anova_tense <- oneway.test(tense ~ factor(room_type), data = data_all, var.equal = FALSE) 
anova_energetic <- oneway.test(energetic ~ factor(room_type), data = data_all, var.equal = FALSE) 

anova_room_type_table <- bind_rows(
  Valence = extract_welch_anova(anova_valence, "Valence"),
  Approach_Avoidance = extract_welch_anova(anova_approach, "Appraoch-avoidance"),
  Tense_Arousal = extract_welch_anova(anova_tense, "Tense Arousal"),
  Energetic_Arousal = extract_welch_anova(anova_energetic, "Energetic Arousal"),
)

knitr::kable(anova_room_type_table, col.names = c("Dependent Variable ", "Numerator DF", "Denominator DF", "F", "p", "Partial EtaSquared"), caption = "Welch's ANOVA results")


```


```{r, echo = FALSE}
# Calculate estimated marginal means for all dependent variables
room_type_model_valence <- lm(valence ~ factor(room_type), data = data_all)
room_type_emm_valence <- emmeans(room_type_model_valence, "room_type", adjust = "games-howell")
room_type_emm_valence_df <- as.data.frame(room_type_emm_valence)

room_type_model_tense <- lm(tense ~ factor(room_type), data = data_all)
room_type_emm_tense <- emmeans(room_type_model_tense, "room_type", adjust = "games-howell")
room_type_emm_tense_df <- as.data.frame(room_type_emm_tense)

room_type_model_energetic <- lm(energetic ~ factor(room_type), data = data_all)
room_type_emm_energetic <- emmeans(room_type_model_energetic, "room_type", adjust = "games-howell")
room_type_emm_energetic_df <- as.data.frame(room_type_emm_energetic)

# Combine all outcomes
emm_table <- bind_rows(
  extract_emm(room_type_emm_valence_df, "Valence"),
  extract_emm(room_type_emm_tense_df, "Tense Arousal"),
  extract_emm(room_type_emm_energetic_df, "Energetic Arousal")
)

knitr::kable(emm_table, col.names = c("Outcome", "Room Type", "Mean (M)", "SE"), caption = "Estimated marginal means (M) and standard errors (SE) by room type")

```

### Figure 4

```{r, echo=FALSE}
# Code to generate figure 4
comparisons <- list(
  c("bedroom", "dining"),
  c("bedroom", "kitchen"),
  c("bedroom", "living room"),
  c("bedroom", "office"),
  c("bedroom", "restaurant"),
  c("dining", "kitchen"),
  c("dining", "living room"),
  c("dining", "office"),
  c("dining", "restaurant"),
  c("kitchen", "living room"),
  c("kitchen", "office"),
  c("kitchen", "restaurant"),
  c("living room", "office"),
  c("living room", "restaurant"),
  c("office room", "restaurant")
)

data_combined <- data_all %>%
  mutate(room_type_grouped = as.character(room_type))
# Make 'Overall' the last factor level so it plots last (rightmost)
data_combined$room_type_grouped <- factor(
  data_combined$room_type_grouped,
  levels = c(setdiff(unique(data_combined$room_type_grouped), "Overall"), "Overall")
)

tick_size <- 15
title_size <- 15
jitter_alpha <- 0.2
jitter_size <- 0.8
box_alpha <- 0.8


plot1 <- ggplot(data_combined, aes(x = room_type_grouped, y = valence)) +
  geom_boxplot(alpha = box_alpha) +
  theme_apa() +
  theme(
    axis.text.x  = element_text(size = tick_size, angle = 45, hjust = 1),
    axis.text.y  = element_text(size = tick_size),
    axis.title.x = element_text(size = title_size, face = "bold"),
    axis.title.y = element_text(size = title_size, face = "bold")
  ) +
  xlab(" ") +
  ylab("Valence") +
  theme(legend.position = "none") +
  scale_x_discrete(labels=NULL) +
  scale_y_continuous(limits = c(-3, 3), breaks = seq(-3, 3, by = 1)) +
  geom_jitter(alpha = jitter_alpha, size = jitter_size)


plot2 <- ggplot(data_combined, aes(x = room_type_grouped, y = approach)) +
  geom_boxplot(alpha = box_alpha) +
  theme_apa() +
  theme(
    axis.text.x  = element_text(size = tick_size, angle = 45, hjust = 1),
    axis.text.y  = element_text(size = tick_size),
    axis.title.x = element_text(size = title_size, face = "bold"),
    axis.title.y = element_text(size = title_size, face = "bold")
  ) +
  xlab(" ") + 
  ylab("Approach-avoidance") +
  theme(legend.position = "none") +
  scale_x_discrete(labels= NULL) +
  scale_y_continuous(limits = c(-3, 3), breaks = seq(-3, 3, by = 1)) +
  geom_jitter(alpha = jitter_alpha, size = jitter_size)


plot3 <- ggplot(data_combined, aes(x = room_type_grouped, y = tense)) +
  geom_boxplot(alpha = box_alpha) +
  theme_apa() +
  theme(
    axis.text.x  = element_text(size = tick_size, angle = 45, hjust = 1),
    axis.text.y  = element_text(size = tick_size),
    axis.title.x = element_text(size = title_size, face = "bold"),
    axis.title.y = element_text(size = title_size, face = "bold")
  ) +
  xlab("Room Type") +
  ylab("Tense Arousal") +
  theme(legend.position = "none") +
  scale_x_discrete(labels=c("bedroom" = "Bedroom", "dining" = "Dining","living room" = "Living room", "office" = "Office",
                            "restaurant" = "Restaurant", "kitchen" = "Kitchen"),
                   guide = guide_axis(angle = 45)) +
  scale_y_continuous(limits = c(-3, 3), breaks = seq(-3, 3, by = 1)) +
  geom_jitter(alpha = jitter_alpha, size = jitter_size)


plot4 <- ggplot(data_combined, aes(x = room_type_grouped, y = energetic)) +
  geom_boxplot(alpha = box_alpha) +
  theme_apa() +
  theme(
    axis.text.x  = element_text(size = tick_size, angle = 45, hjust = 1),
    axis.text.y  = element_text(size = tick_size),
    axis.title.x = element_text(size = title_size, face = "bold"),
    axis.title.y = element_text(size = title_size, face = "bold")
  ) +
  xlab("Room Type") +
  ylab("Energetic Arousal") +
  theme(legend.position = "none") +
  scale_x_discrete(labels=c("bedroom" = "Bedroom", "dining" = "Dining","living room" = "Living room", "office" = "Office",
                            "restaurant" = "Restaurant", "kitchen" = "Kitchen"),
                   guide = guide_axis(angle = 45)) +
  scale_y_continuous(limits = c(-3, 3), breaks = seq(-3, 3, by = 1)) +
  geom_jitter(alpha = jitter_alpha, size = jitter_size)

# Arrange plots without legends
plots_grid <- plot_grid(plot1, plot2, plot3, plot4, ncol = 2, rel_heights = c(1, 1))

# Combine plots grid with the legend on the right side
#final_plot <- plot_grid(plots_grid, rel_widths = c(4, 0))
# Above code for saves plots with different sizes. This fixes that. 
library(patchwork)
final_plot <- (plot1 + plot2) / (plot3 + plot4)

# Display
print(final_plot)
ggsave(file=".\\Visualizations\\room_type.svg", plot=final_plot, width=12, height=10, dpi = 100)

```

# Appendix 

## Section S4. Results of all regression models created in the study

### Results Regression TfV

Model 2 TfV:

```{r, echo = FALSE}
regression_table(model2_t_v)
```

Model 3 TfV:

```{r, echo = FALSE}
regression_table(model3_t_v)
```

Model 4 TfV:

```{r, echo = FALSE}
regression_table(model4_t_v)
```

Model 5 TfV:

```{r, echo = FALSE}
regression_table(model5_t_v)
```

Model 6 TfV:
```{r, echo = FALSE}
regression_table(model6_t_v)
```

Model 7 TfV:
```{r, echo=FALSE}
flextable::as_flextable(model7_t_v)
```

### Results Regression VfT

Model 2 VfT:

```{r, echo = FALSE}
regression_table(model2_v_t)
```

Model 3 VfT:

```{r, echo = FALSE}
regression_table(model3_v_t)
```

Model 4 VfT:

```{r, echo = FALSE}
regression_table(model4_v_t)
```

Model 5 VfT:

```{r, echo = FALSE}
regression_table(model5_v_t)
```

Model 6 VfT:

```{r, echo = FALSE}
regression_table(model6_v_t)
```

Model 7 VfT:
```{r, echo=FALSE}
flextable::as_flextable(model7_v_t)
```

### Results Regression Efv

Model 2 Efv:

```{r, echo = FALSE}
regression_table(model2_e_v)
```

Model 3 Efv:

```{r, echo = FALSE}
regression_table(model3_e_v)
```

Model 4 Efv:

```{r, echo = FALSE}
regression_table(model4_e_v)
```

Model 5 Efv:

```{r, echo = FALSE}
regression_table(model5_e_v)
```

Model 6 Efv:

```{r, echo = FALSE}
regression_table(model6_e_v)
```

Model 7 EfV:
```{r, echo=FALSE}
flextable::as_flextable(model7_e_v)
```


### Results Regression VfE

Model 2 VfE:

```{r, echo = FALSE}
regression_table(model2_v_e)
```

Model 3 VfE: 

```{r, echo = FALSE}
regression_table(model3_v_e)
```

Model 4 VfE:

```{r, echo = FALSE}
regression_table(model4_v_e)
```

Model 5 VfE:

```{r, echo = FALSE}
regression_table(model5_v_e)
```

Model 6 VfE:

```{r, echo = FALSE}
regression_table(model6_v_e)
```

Model 7 VfE:
```{r, echo=FALSE}
flextable::as_flextable(model7_v_e)
```

### Results Regression EfT

Model 2 EfT:

```{r, echo = FALSE}
regression_table(model2_e_t)
```

Model 3 EfT:

```{r, echo = FALSE}
regression_table(model3_e_t)
```

Model 4 EfT:

```{r, echo = FALSE}
regression_table(model4_e_t)
```

Model 5 VfT:

```{r, echo = FALSE}
regression_table(model5_e_t)
```

Model 6 EfT:

```{r, echo = FALSE}
regression_table(model6_e_t)
```

Model 7 EfT:
```{r, echo=FALSE}
flextable::as_flextable(model7_e_t)
```

### Results Regression TfE

Model 2 TfE:

```{r, echo = FALSE}
regression_table(model2_t_e)
```

Model 3 VfT:

```{r, echo = FALSE}
regression_table(model3_t_e)
```

Model 4 TfE:

```{r, echo = FALSE}
regression_table(model4_t_e)
```

Model 5 TfE:

```{r, echo = FALSE}
regression_table(model5_t_e)
```

Model 6 TfE:

```{r, echo = FALSE}
regression_table(model6_t_e)
```

Model 7 TfE:
```{r, echo=FALSE}
flextable::as_flextable(model7_t_e)
```

## Section S6 Pairwise comparisons for each room type

### Section S6.1. Pairwise comparison of valence between each room types:

```{r, echo=FALSE}
rempsyc::nice_table(data.frame(pairs(room_type_emm_valence)))
```

### Section S6.2. Pairwise comparison of tense arousal between each room types:

```{r, echo = FALSE}
rempsyc::nice_table(data.frame(pairs(room_type_emm_tense)))

```

### Section S6.3. Pairwise comparison of energetic arousal between each room types:

```{r,echo = FALSE}
rempsyc::nice_table(data.frame(pairs(room_type_emm_energetic)))

```
